
---
title: "K-Nearest Neighbours in R"
output: word_document
---

 CMTH 642 Course

```{r setup, include=FALSE}
library("class")
library("gmodels")
```

We will be using the iris data set for this example.
```{r}
data(iris)
head(iris)
str(iris)
```

Let's split the iris dataset into training and test set.
```{r}
train_index <- sample(1:nrow(iris), 0.7 * nrow(iris))
train.set <- iris[train_index,]
test.set  <- iris[-train_index,]
```

Now, we remove the Species column from our training and test datasets.
```{r}
train.set_new <- train.set[-5]
test.set_new <- test.set[-5]
```

Now, we store the labels from our training and test datasets.
```{r}
iris_train_labels <- train.set$Species 
iris_test_labels <- test.set$Species
```

For k=3, let's make our prediction on the test set.
```{r}
iris_knn_prediction <- knn(train = train.set_new, test = test.set_new, cl= iris_train_labels, k = 3) 
```

Let's see the confusion matrix.
```{r}
CrossTable(x=iris_test_labels, y=iris_knn_prediction, prop.chisq=FALSE)
```

For k=11, let's make our prediction on the test set.
```{r}
iris_knn_prediction <- knn(train = train.set_new, test = test.set_new, cl= iris_train_labels, k = 11) 
```

Let's see the confusion matrix.
```{r}
CrossTable(x=iris_test_labels, y=iris_knn_prediction, prop.chisq=FALSE)
```
